### 2020-07-10 README.Rmd
transition to 0.1.8 and moving functionality to retroharmonize

The goal of `eurobarometer` is converting Eurobarometer microdata files, as stored by GESIS, into tidy R data frames and help common pre-processing problems.

@@

5. The [eurobarometer_labelled](http://eurobarometer.danielantal.eu/articles/eurobarometer_class.html) class comes with simple methods that can convert all variables to the base R types of numeric or factor, and they are ready to be used with any R statistical packages and tidyverse data processing tools. Alternatively, they can be exported back to [SPSS](https://haven.tidyverse.org/reference/read_spss.html) or [Stata](https://haven.tidyverse.org/reference/read_dta.html) files with the functions of the [haven](https://haven.tidyverse.org/) package.

>>>>

The goal of `eurobarometer` is converting Eurobarometer microdata files, as stored by GESIS, into tidy R data frames and help common pre-processing problems. The more generic function for retrospecitve (ex post) survey harmonization can be found in the package [retroharmonize](http://retroharmonize.satellitereport.com/).

@@
